HUME: Human UCCA-based Machine-Translation Evaluation

### 2016-03-09 paper/main.tex
some notes

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{subfigure}
\usepackage{pgfplotstable}
\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}

@@

\subsection{Annotation Guidelines}\label{sec:guidelines}

@@

\subsection{Annotation Process}
\begin{itemize}
  \item Numbers of annotators, IDs
  \item Length of annotation, timings
  \item Sentences annotated
\end{itemize}

For the annotation process, we recruited seven annotators, two for each of the target languages apart from Czech. They were
all native speakers of the target languages and fluent in English. For Czech, we also recruited a  group of additional annotators
to annotate small numbers of sentences each for the purpose of calculating inter-annotator agreement. In \tabref{tab:annot}
we show the total number of sentences and nodes annotated by each annotator, where we consider the additional Czech
annotators as a single annotator.

@@

To calculate Kappa, we consider the annotation task as a classification task on 
nodes. We only consider nodes where there are at least two annotations from different
annotators and we treat nodes with more than two annotations as a set of paired
annotations\bh{This may not be correct, so should/could we do Kappa across the 
variable multiple annotations on Czech}. We consider Kappa separately on the lexical
nodes (annotated as red, orange or green) and the structural nodes (annotated
as acceptable or bad) since there should not be any confusion between these two types of
nodes. The small number of nodes which one annotator had labelled as structural and 
the other as lexical were ignored for the purposes of IAA, since such cases of annotator 
error could be caught by improved tool support.  The Kappas are shown in \tabref{tab:iaa}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & & & & \\
\hline
Lexical nodes & & & & \\
Kappa & & & & \\
\hline
Structural nodes & & & & \\
Kappa & & & & \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

To assess whether, as we hoped, HUME would make it easier to reliably annotate long sentences,
we binned the sentences according to length and measured Kappa on each of the bins.

>>>>

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
%\usepackage{subfigure}
\usepackage{pgfplotstable}
\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}

@@

\subsection{Annotation Guidelines}\label{sec:guidelines}
In this section we summarise the procedure for annotating machine translation output.

@@

\subsection{Annotation Process}

For the annotation of the machine translation, we recruited seven annotators, two for each of the target languages apart from Czech. They were
all native speakers of the target languages and fluent in English. For Czech, we also recruited a  group of additional annotators
to annotate small numbers of sentences each for the purpose of calculating inter-annotator agreement. In \tabref{tab:annot}
we show the total number of sentences and nodes annotated by each annotator, where we consider the additional Czech
annotators as a single annotator.

\emph{Show numbers of annotations, and timings}

\emph{Describe the UCCA annotation}

@@

To calculate Kappa, we consider the annotation task as a classification task on 
nodes. We only consider nodes where there are at least two annotations from different
annotators and we treat nodes with more than two annotations as a set of paired
annotations\bh{This may not be correct, so should/could we do Kappa across the 
variable multiple annotations on Czech}. We consider Kappa separately on the lexical
nodes (annotated as red, orange or green) and the structural nodes (annotated
as acceptable or bad) since there should not be any confusion between these two types of
nodes. The small number of nodes which one annotator had labelled as structural and 
the other as lexical were ignored for the purposes of IAA, since such cases of annotator 
error could be caught by improved tool support.  The Kappas are shown in \tabref{tab:iaa}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & & 102 & 334 & 217 \\
\hline
Lexical nodes & & 1724 & 5386 & 3570 \\
Kappa & & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & & 1040 & 2655 & 1989 \\
Kappa & & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

To assess whether, as we hoped, HUME would make it easier to reliably annotate long sentences,
we binned the sentences according to length and measured Kappa on each of the bins. Each bin covers
a length range of 10, and we show the variance of kappa with length in \figref{fig:iaalength}.\bh{Note that cs is missing}

\def\iaafig #1{\includegraphics[width=7cm]{iaa_length_#1.png}}

\begin{figure*}[ht!]
\begin{tabular}{cc}

\subfloat[English-Czech]{
  \iaafig{de}
}
&
\subfloat[English-German]{
  \iaafig{de}

}
\\

\subfloat[English-Polish]{
  \iaafig{pl}

}
&
\subfloat[English-Romanian]{
  \iaafig{ro}

}
\end{tabular}
\caption{Inter-annotator Agreement (Kappa) versus sentence length, separately for
structural and lexical nodes. }
\label{fig:iaallength}

\end{figure*}
